%% start of file `christian-pena_cv.tex'.
%% Christian Pena CV
%%
%% Adapted from moderncv template.tex
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.815]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\definecolor{blue}{RGB}{26,13,171}

% personal data
\firstname{Christian}
\familyname{Pena Valerio}

\phone[mobile]{+1~(646)~799~7754}
\email{khrizpv@gmail.com}
\homepage{christianpv.com}
\social[linkedin]{christian-pena-valerio}
\social[twitter]{khrizpv}
\social[github]{christianpv}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Experience}

\cventry
  {February 2017 - Present}
  {Full Stack Software Engineer}
  {\textmd{\href{https://learnwithhomer.com}{\textcolor{blue}{Homer(acquired by Speakaboos)}}}}
  {\textmd{New York, NY - Remote}}{}
  {
    Improved performance on the webapp by doing HTTP optimizations.
    Worked on the user onboarding for the webapp with JavaScript, React, and Jest.
    Built content API with GraphQL, TypeScript, Node.js, Koa, Jest, Docker, and Redis.
    Developed CMS backend with Node.js, Express, Mocha, and S3.
    Made the CI pipelines for testing the CMS/API, processing assets, and deploying to staging/production using Jenkins, Groovy, Node.js, and Elastic Beanstalk.
  }

\cventry
  {February 2016 - January 2017}
  {Front End Software Engineer}
  {\textmd{\href{https://www.speakaboos.com}{\textcolor{blue}{Speakaboos}}}}
  {\textmd{New York, NY}}{}
  {
    Developed the parent/teacher dashboard by using JavaScript, React, CSS Modules, D3.js, and SVG.
    Improved conversion by running A/B tests while working on the redesign of the webapp.
    Incrementally refactor the webapp with Node.js, JavaScript, React, and CSS Modules.
    Created a visual style guide by using HTML, Sass, and JavaScript.
  }

\cventry
  {July 2015 - January 2016}
  {Full Stack Web Developer}
  {\textmd{Freelance}}
  {\textmd{Remote}}{}
  {
    \begin{itemize}
    \item Anime Center -
      Fixed upcoming episode, anime pagination, latest episode link on each anime page, anime relations, and caching system.
      Rewrote most of the backend with the Laravel PHP framework.
      Redesigned the MySQL schema, added foreign keys, renamed columns to be more descriptive, and removed unnecessary/duplicate data.
    \item Country Lyrics -
      Made the MySQL schema, the PHP backend with Laravel, the Python scraper with Scrapy, and the frontend with Sass/JavaScript.
      Used the Youtube API to attach songs to lyrics.
      Contributed to plyr, an open source media player, to convert the LESS files to Sass.
    \end{itemize}
  }

\cventry
  {January 2015 - June 2015}
  {Front End Web Developer}
  {\textmd{\href{http://bitbang.cl}{\textcolor{blue}{BitBang Estudio Digital}}}}
  {\textmd{Santiago, Chile}}{}
  {
    Developed the frontend for the single page applications \href{http://bitbang.cl/portafolio/plato-de-america/}{\textcolor{blue}{Plato de America}}, and \href{http://bitbang.cl/portafolio/apuesto-por-chile/}{\textcolor{blue}{Apuesto por Chile}} using HTML, Sass, and JavaScript.
    Built \textmd{\href{http://www.latamfactors.cl}{\textcolor{blue}{Latam Factors}}}, and \textmd{\href{http://www.cchc.cl}{\textcolor{blue}{CChC}}} using HTML, Sass, JavaScript, and PHP.
    Developed the \href{http://abrilintranet.cl/}{\textcolor{blue}{Abril Intranet}} frontend using HTML, Sass, and JavaScript.
  }

\cventry  
  {July 2014 - December 2014}
  {Web Developer}
  {\textmd{\href{http://bucarestart.cl}{\textcolor{blue}{Bucarest Art}}}}
  {\textmd{Santiago, Chile}}{}
  {
    Increased revenue by enhancing SEO.
    Built a custom WordPress theme, and plugins to add new functionality using HTML, Sass, PHP, and JavaScript.
  }

\cventry
  {January 2014 - June 2014}
  {Web Developer}
  {\textmd{Freelance}}
  {\textmd{Remote}}{}
  {
    Mainly work with HTML, Sass, JavaScript, and PHP to built \textmd{\href{http://bucarestart.cl}{\textcolor{blue}{Bucarest Art}}},
    \textmd{\href{https://web.archive.org/web/20160306131956/http://comproantiguedades.cl/}{\textcolor{blue}{Compro Antiguedades}}},
    and \textmd{\href{http://www.clinicaloscoihues.cl/}{\textcolor{blue}{Clinica los Coihues}}}.
    Fixed a couple bugs and added new features to the \textmd{\href{http://www.sietecomunicaciones.cl/}{\textcolor{blue}{Siete Comunicaciones}}} website.
  }

\section{Skills}
\cvitem{Programming Languages}{HTML, CSS, Sass, JavaScript, TypeScript, PHP, Python}
\cvitem{Query Languages}{GraphQL, SQL, Xpath}
\cvitem{Databases}{MySQL, Redis, MongoDB}
\cvitem{AWS}{Route 53, EC2, S3, Elastic Beanstalk, ElastiCache}
\cvitem{Frameworks, Libraries, and Tools}{Node.js, React, Webpack, Babel, D3.js, Express, Koa, Yarn, Jest, Mocha, Bootstrap, Eslint, Prettier, Jenkins, Nginx, Docker}
\cvitem{Knowledge}{MVC, OOP, DRY, KISS, RWD, UX, CLI, A/B Testing, ORM, SEO, HTTP, SVG}
\end{document}